### 2019-03-04 README.Rmd
reproducibility sweep and DOI

## Docker

@@

>>>>

### Repository structure

The repository is structured as an R package. It has the following structure:

- **data-raw:** Raw data processing.
- **data:** Processed data.
- **R:** Supporting R functions
- **vignettes:** Analysis paper and results.

### Manual install

- Install R (analysis run with `3.5.2`) and Rstudio.

- Download the analysis folder from [https://github.com/seabbs/DirectEffBCGPolicyChange/archive/master.zip](https://github.com/seabbs/DirectEffBCGPolicyChange/archive/master.zip) or use `git clone`, as follows, in the command line (not the R terminal).

```{bash clone-package, eval = FALSE}
git clone https://github.com/seabbs/DirectEffBCGPolicyChange.git
```

- Once this has been downloaded click on the project file (`DirectEffBCGPolicyChange.Rproj`).

- Install the analysis dependencies and build the package using the following. To enable more robust reproducibility consider using the [`checkpoint`](https://cran.r-project.org/web/packages/checkpoint/index.html) package versioned locked to R `3.5.2`.

```{r get-packages, eval = FALSE}

#install.packages("devtools")

# To build locally
devtools::install_dev_deps(dependencies = TRUE)
devtools::install()

# Alternatively to remote install
devtools::install_github("seabbs/DirectEffBCGPolicyChange", dependencies = TRUE)
```

- Load the analysis results by running `vignettes/paper.Rmd`. The complete analysis is not reproducible as the raw data cannot be published, however all interim results are stored in the repository (`data`) and these can be explored.

- Alternatively the complete analysis (along with documentation) can be reconstructed using `make` in the project root directory.

### Docker

@@

Alternatively the analysis environment can be accessed via [binder](https://mybinder.org/v2/gh/seabbs/DirectEffBCGPolicyChange/master?urlpath=rstudio).
